Parsing Tweets into Universal Dependencies

### 2017-09-26 paper.tex
sync

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\newcommand\BibTeX{B{\sc ib}\TeX}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=1em]{12}{14}{nmod}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.45em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.35em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 96.6 \\
		Twokenizer & 94.4 \\
		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 (re-trained) & 97.3 \\
		Our Tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{The tokenization results.}\label{tbl:tok-result}
\end{table}

We test our tokenizer on Tweebank v2 test set.
F-score was used to evaluate the tokenization accuracy.
Our model was trained on a merge of UD\_English and Tweebank v2 training data.
Table \ref{tbl:tok-result} shows the tokenization results along with comparison with other tokenizers.
Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
By comparing the rule-based group to the model-based group, we can see the model-based ones generally outperform the rule-based tokenizers, which shows the necessity of using statistical model for tweet tokenization.

@@

Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
We use the postagger of \newcite{owoputi-EtAl:2013:NAACL-HLT}.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & P \\
		\hline
		Stanford Postagger & 65.6 \\
		Stanford Postagger (re-train) & 90.4 \\
		UD pipe v1.2 & 78.7 \\
		UD pipe v1.2 (re-trained) & 83.8 \\
		bi-LSTM & 91.8 \\
		ARK Tagger & \bf 95.1 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
\end{table}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 92.0 \\
		Our Tokenizer & 93.6 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on automatic tokenization. The POS tagger we used is from Owoput et al., 2013.}\label{tbl:pos-result-vs-tok}
\end{table}

We test several different POS taggers on Tweebank v2.
We also study the influence of tokenization on POS-tagging by evaluating the model's performance on automatically tokenized data.
This result is shown in Table \ref{tbl:pos-result-vs-tok}.

@@

%Time is a major concern on
Social media applications usually require processing tones of data.
Speed becomes important under such circumstance.
In this paper, we use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016}, which can parse a sentence in linear time and harness the useful character representations.
To further improve the parsing accuracy, we propose a new method to distill an ensemble of 20 differently initialized parsers into one greedy parser.

Distilling a smaller classifier from a single large neural network was explored in \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016}.
In these works, the predicted distribution from the larger model serves as a soft target for training the small classifier.
Training the smaller classifier is delivered by training with a interpolate between two losses:
\begin{equation}\label{eq:distill}
\mathcal{L}=(1-\alpha)\mathcal{L}_{NNL} + \alpha\mathcal{L}_{KD}
\end{equation}
where $\mathcal{L}_{NNL}$ is the traditional log-likelihood loss and $\mathcal{L}_{KD}$ is the loss from soft target.

@@

In this paper, we follow \newcite{DBLP:journals/corr/HintonVD15} and \newcite{kim-rush:2016:EMNLP2016} and distill one single parser from 20 parsers trained with different initialization.
Training a transition-based greedy parser includes generating a transition sequence from the data and learning the classifier from the states in the sequence.
And it also holds for training the ensemble parser.
%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).

@@

We show the effect of $\alpha$ in Figure \ref{fig:effect-alpha}.
This figure shows that parsers with larger $\alpha$ achieves better performance than that with smaller $\alpha$.
This result shows that learning from the hard target in unnecessary.

%\paragraph{Effect of $\mathcal{T}$}
%
%\begin{figure}[t]
%	\centering
%	\includegraphics[width=\columnwidth]{graphics/temperature}
%	\caption{The effect of temperature $\alpha$.}\label{fig:effect-temp}
%\end{figure}

\paragraph{Results}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 79.25 & 74.17 \\
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.90 & 72.95 \\
		Ensemble 20 & 82.80 & 78.69 \\
		Distill expert ($\alpha$=0.)& 81.22 & 76.98 \\
		Distill boltzmann ($\mathcal{T}$=1) & 81.55 & 77.32 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result.}\label{tbl:parse-result}
\end{table}

%\subsection{Exploiting UD\_English}

%UD\_English as an important source of training data.
%\section{Model}
%We propose a new model

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}

@@

\begin{figure*}[t]
	\centering
	\small
	\begin{dependency}[edge slant=2, text only label, label style=above]
		\begin{deptext}
			@username \& its \& \#awesome \& u \& gonna \& $\heart$ \& it \& Chk \& out \& our \& cooool \& project \& on \& http:// \& + \& RT \& pls\\
			\tiny PROPN \& \tiny PRON \& \tiny ADJ \& \tiny PRON \& \tiny VERB \& \tiny VERB \& \tiny PRON \& \tiny VERB \& \tiny ADP \& \tiny PRON \& \tiny ADJ \& \tiny NOUN \& \tiny ADP \& \tiny X \& \tiny SYM \& \tiny VERB\& \tiny INTJ\\
		\end{deptext}
		\deproot{3}{root}
		\depedge[edge unit distance=1em]{3}{1}{vocative}
		\depedge[edge unit distance=1em]{3}{2}{nsubj}
		\depedge[edge unit distance=1em]{3}{5}{parataxis}
		\depedge[edge unit distance=1em]{5}{4}{nsubj}
		\depedge[edge unit distance=1em]{5}{6}{xcomp}
		\depedge[edge unit distance=1em]{6}{7}{obj}
		\depedge[edge unit distance=0.7em]{3}{8}{parataxis}
		\depedge[edge unit distance=1em]{8}{9}{compound:prt}
		\depedge[edge unit distance=0.7em]{8}{12}{obj}
		\depedge[edge unit distance=1em]{12}{10}{nmod:poss}
		\depedge[edge unit distance=1em]{12}{11}{amod}
		\depedge[edge unit distance=0.6em]{8}{14}{obl}
		\depedge[edge unit distance=1em]{14}{13}{case}
		\depedge[edge unit distance=0.55em]{8}{16}{conj}
		\depedge[edge unit distance=1em]{16}{15}{cc}
		\depedge[edge unit distance=0.37em]{3}{17}{discourse}
	\end{dependency}
	\caption{An example tweet with informal but syntactic tokens.}\label{fig:informal-toks}
\end{figure*}

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 96.6 \\
		Twokenizer & 94.4 \\
% 		UD pipe v1.2 & 94.7 \\
		UD pipe v1.2 & 97.3 \\
		Our bi-LSTM tokenizer & \bf 98.3 \\
		\hline
	\end{tabular}
	\caption{The tokenization results.}\label{tbl:tok-result}
\end{table}

We test our tokenizer on Tweebank v2 test set. F-score was used to evaluate
the tokenization accuracy. Our model was trained on a merge of UD\_English
and Tweebank v2 training data. Table \ref{tbl:tok-result} shows the
tokenization results along with comparison with other tokenizers. UD pipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same data.
Our bi-LSTM tokenizer achieves the best accuracy among all these tokenizers.
From this table, we can also see that the model-based tokenizers
generally outperform the rule-based tokenizers, which shows the necessity of
using statistical model for tweet tokenization.

@@

Part-of-Speech tagging for tweets has been studied in previous literals \cite{ritter-EtAl:2011:EMNLP,gimpel-EtAl:2011:ACL-HLT2011,owoputi-EtAl:2013:NAACL-HLT,gui-EtAl:2017:EMNLP20172}.
The goal is to give a fair comparison of these models on our annotation.
We are especially interested in finding out the can neural network
models win against the model enhanced by carefully crafted features.

@@

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & P \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford Postagger & 90.4 \\
%		UD pipe v1.2 & 78.7 \\
		ARK tagger (greedy) & 94.2 \\
		ARK Tagger (CRF) & \bf 95.1 \\
		\hdashline
%		UD pipe v1.2 & 83.8 \\
		\newcite{ma-hovy:2016:P16-1} & \\
		Our word bi-LSTM & 89.1 \\
		Our char bi-LSTM + word bi-LSTM & 91.4 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on gold tokenization.}\label{tbl:pos-result}
\end{table}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rc}
		\hline
		\it System & F \\
		\hline
		Stanford Tokenizer & 92.0 \\
		Our Tokenizer & 93.6 \\
		\hline
	\end{tabular}
	\caption{The POS tagging result on automatic tokenization.}\label{tbl:pos-result-vs-tok}
\end{table}

We test the POS taggers on Tweebank v2 test set and the results are shown in
Table \ref{tbl:pos-result}. All the comparison systems were re-trained on
the merge of UD\_English and Tweebank v2 training set.
Gold tokenization was used. This table shows that carefully feature engineer
POS tagger \cite{owoputi-EtAl:2013:NAACL-HLT} outperform the neural network
models.

We also study the influence of tokenization on POS tagging
by evaluating the model's performance on automatically
tokenized data. We use the best performed POS tagger \cite{owoputi-EtAl:2013:NAACL-HLT}
on gold tokenization as our POS tagger. The results are
shown in Table \ref{tbl:pos-result-vs-tok}. Table \ref{tbl:pos-result-vs-tok}
shows that tokenization errors propagate to POS tagging but these
errors didn't significant influence the tagging decisions.

@@

%Time is a major concern on
Social media applications usually require processing tones of data.
Speed becomes important under such circumstance. In this paper, we
use the neural greedy parser by \newcite{ballesteros-EtAl:2016:EMNLP2016},
which can parse a sentence in linear time and harness the useful
character representations. To further improve the parsing accuracy,
we propose a new method to distill an ensemble of 20 differently
initialized parsers into one parser.

Distilling a simple and fast {\it student model} from the accurate but
slow {\it teacher model} was explored in \newcite{DBLP:journals/corr/HintonVD15}
and \newcite{kim-rush:2016:EMNLP2016}. In their works, the predicted
distribution from the teacher model serves as a soft target for
training the student model by minimizing
\begin{equation}
\mathcal{L}_{KD} = \sum_k q(y=k|x) p(y=k|x)
\end{equation} where $q(y=k|x)$ is the probability distribution
predicted by the teacher model. Training the student model is
delivered by training with a interpolate between two losses:
\begin{equation}\label{eq:distill}
\mathcal{L}=(1-\alpha)\mathcal{L}_{NNL} + \alpha\mathcal{L}_{KD}
\end{equation}
where $\mathcal{L}_{NNL}$ is the negative log-likelihood loss.

@@

The generic algorithm for training a transition-based greedy parser
usually includes 1) generating a sequence of transitions from the 
training data with ``oracle'' and 2) learning the classifier from
the transitions. One natural adoption of the distillation will be replacing
$\mathcal{L}_{NLL}$ with the distillation objective (Equation \ref{eq:distill})
in the second step. We name such method as {\it distill expert}. 
We adopt such distilling method in our preliminary experiments.

\paragraph{Preliminary Results}
In our preliminary experiments, we train our parser on the merge of UD\_English
and Tweebank v2 training set. Automatic POS tags are assigned with 5-fold
jackknifing. Hyper-parameters including the value of $\alpha$ in Equation \ref{eq:distill}
are tuned on Tweebank v2 development set. The 20 parsers are trained with
different random seeds and ensembled by averaging their output probability
distribution. The ensemble parser achieves a LAS of 78.8, which is more 
than 3 points higher than the baseline single parser. Distilling from this
parser leads to a single parser of 77.0 LAS.
%We first study the necessity of log-likelihood loss (the first term in Equation \ref{eq:distill}).

@@

We further study the effect of $\alpha$ by varying it from 0 to 1 and
the results are shown in Figure \ref{fig:effect-alpha}. From this figure,
we can see that distilling parsers with larger $\alpha$ achieves better
performance, which means the model should pay more attention to learn
from the teacher model. And the changes of $\alpha$ from 0.9 to 1.0
didn't significantly influence the final result, which casts a doubt on
the necessity of learning from $\mathcal{L}_{NNL}$.

\paragraph{Learning from Exploration} We further set $\alpha$ to 1.0
and this enable us to get rid of the ``oracle'' in the first step in generic
transition-based parser training algorithm. Instead of generating
training instances from the oracle, we generate them by random sampling
transition from the teacher model's output distribution and follow the
trajectory of these transitions. We name such method as {\it distill explore}.

\paragraph{Final Results}
\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.4 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble 20x & 83.0 & 78.8 \\
		Distill 20x expert ($\alpha$=1.0) & 81.2 & 76.7 \\
		Distill 20x expert ($\alpha$=0.9) & 81.4 & 77.0 \\		
		Distill 20x explore & 82.2 & 77.9 \\
		\hline
	\end{tabular}
	\caption{The parsing results on automatic POS tags.}\label{tbl:parse-result}
\end{table}

\begin{table}[t]
	\centering
	\small
	\begin{tabular}{rcc}
		\hline
		\it System & UAS & LAS \\
		\hline
		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 93.0 & 90.9 \\
		%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		Ensemble 20x & 94.5 & 92.6 \\
		Distill 20x expert ($\alpha$=1.0) & 93.8 & 91.7 \\
		Distill 20x explore & 94.1 & 92.0 \\
		\hline
		\newcite{kuncoro-16} & 94.3 & 92.1 \\
		\hline
	\end{tabular}
	\caption{Distillation on PTB.}\label{tbl:parse-result-PTB}
\end{table}

Our final parsing experiments are shown in Table \ref{tbl:parse-result},
in which we can see that distilling from exploration significant outperform
distilling from expert by achieving one more point LAS improvement.
Additional experiments on the Penn Treebank data are performed following
the setting of \newcite{dyer-EtAl:2015:ACL-IJCNLP} and similar trend are
witnessed. We address this improvement to the fact that learning
from exploration enables the single parser to learn from the ensemble on
states of different qualities.

\subsection{Final Evaluation}
Finally, we evaluate the tweet parsing in a pipeline manner.
